Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-07-11 manuscripts/manuscript.Rmd
minor figure tweaks

```{r figure_5, dependson=c("sim"), fig.cap="In the management context, GPDP outperforms approaches based on parametric models. We show 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model.", fig.width=6, fig.height=6}
ggplot(sims_data) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=0.1) +
  scale_colour_manual(values=colorkey) + 
  facet_wrap(~method) + guides(legend.position="none")

@@

```{r figure_7, fig.width=6, dependson=c("sensitivity-trends"), fig.cap="The effect of increasing noise or decreasing Allee threshold levels on the net present value of the fishery when managed under the GPDP, relative to managing under the true model (with known parameters).  Other than the focal parameter (stochasticity, Allee threshold), other parameters are held fixed as above to illustrate this effect."}

plot_sigmas <- ggplot(vary_sigma, aes(noise, value)) + 
  geom_point() + ylab("Net present value") + 
  xlab("Level of growth stochasticity") + theme_bw() 
plot_allees <- ggplot(vary_allee, aes(allee, value)) + 
  geom_point()+ ylab("Net present value") + 
  xlab("Allee threshold stock size") + theme_bw()

multiplot(plot_sigmas, plot_allees, cols=2)

write.csv(vary_sigma, "components/data/vary_sigma.csv")
write.csv(vary_allee, "components/data/vary_sigma.csv")
```

>>>>

```{r figure_5, dependson=c("sim"), fig.cap="In the management context, GPDP outperforms approaches based on parametric models. We show 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model.", fig.width=6, fig.height=6}
ggplot(sims_data) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=0.1) +
  scale_colour_manual(values=colorkey, guide = guide_legend(override.aes = list(alpha = 1))) + 
  facet_wrap(~method) + guides(legend.position="none")

@@

```{r figure_7, fig.width=6, fig.height=3, dependson=c("sensitivity-trends"), fig.cap="The effect of increasing noise or decreasing Allee threshold levels on the net present value of the fishery when managed under the GPDP, relative to managing under the true model (with known parameters).  Other than the focal parameter (stochasticity, Allee threshold), other parameters are held fixed as above to illustrate this effect."}
plot_sigmas <- ggplot(vary_sigma, aes(noise, value)) + 
  geom_point() + ylab("Net present value") + 
  xlab("Level of growth stochasticity") + theme_bw() 
plot_allees <- ggplot(vary_allee, aes(allee, value)) + 
  geom_point()+ ylab("Net present value") + 
  xlab("Allee threshold stock size") + theme_bw()
multiplot(plot_sigmas, plot_allees, cols=2) 
write.csv(vary_sigma, "components/data/vary_sigma.csv")
write.csv(vary_allee, "components/data/vary_sigma.csv")
```
